Multiplex stream graphs

### 2019-04-16 tex/main.tex
Update main.tex. Ajout de suggestions pour intra et inter layer.

    We define a multiplex stream graph as a tuple $M = (T_M, V_M, W_M, E_M, T, V, {\cal L})$, such that $T_M \subseteq T$, $V_M \subseteq V \times {\cal L}$, $W_M \subseteq T_M\times V_M$ and $E_M\subseteq T_M \times V_M \otimes V_M$.
    $T$ and $V$ are, respectively, a time interval and a set of nodes, just like in stream graphs.
    We then define {\em layers}; a multiplex stream graph can have an arbitrary number $d$ of aspects, and we define ${\cal L}$, as $\{L_i\}_{i=0}^{d}$ thset of layers, such that there is one layer for each $i=0..d$.
    Notice that just like in multiplex networks, nodes in time ({\em i.e.}, elements of $W_M$) can be present in an arbitrary number of layers.

@@

@@

    For any two layers $i,j\in {\cal L}$, the {\em inter-layer} stream graph $S^{(i,j)}$ ...

    Notice that for any layer $i$, $S^{(i)}$ is equivalent to $S^{(i,j)}$.

>>>>

    We define a multiplex stream graph as a tuple $M = (T_M, V_M, W_M, E_M, T, V, {\cal L})$, such that $T_M \subseteq T$, $V_M \subseteq V \times {\cal L}$, $W_M \subseteq T_M\times V_M$ and $E_M\subseteq T_M \times V_M \otimes V_M$.
    $T$ and $V$ are, respectively, a time interval and a set of nodes, just like in stream graphs.
    We then define {\em layers}; a multiplex stream graph can have an arbitrary number $d$ of aspects, and we define ${\cal L}$, as $\{L_i\}_{i=0}^{d}$ the set of layers, such that there is one layer for each $i=0..d$.
    Notice that just like in multiplex networks, nodes in time ({\em i.e.}, elements of $W_M$) can be present in an arbitrary number of layers.

@@

	\pimprenelle{Il y a une subtilité sur les layers : an aspect $(i)$ is a set $L_i$ of  elementary layers $\alpha^{i}_1,\dots,\alpha^{i}_n$
    		 a layer $\alpha$ is an combination of elementary layer of each aspect : $\alpha \in L_1\times\dots\times L_d$
   	}

@@

	\pimprenelle{Suggestion :}
	For any layer $\alpha \in L_1 \times \dots \times L_d$, the {\em intra-layer} stream graph $S^{\alpha}$ is the stream $S^{\alpha}=(T,V^{\alpha},W^{\alpha},E^{\alpha})$ such that for all $t$ in T :
	\begin{itemize}
		\item $V^{\alpha}$ is the set of nodes $(u,\alpha) \in V_M$
		\item $W^{\alpha}$ is the set of $(t,u,\alpha)$ included in $W_M$. 
		\item $E^{\alpha}$ is the set of links $(t,(u,\alpha),(v,\alpha))$ included in $E_M$.		
	\end{itemize}
	\pimprenelle{fin}

    For any two layers $i,j\in {\cal L}$, the {\em inter-layer} stream graph $S^{(i,j)}$ ...
	\pimprenelle{Suggestion}
	For any two layers $\alpha, \beta \in L_1\times \dots\times L_d$, the {\em inter-layer} stream graph is the stream $S^{\alpha,\beta} = (T, V^{(\alpha,\beta)},W^{(\alpha,\beta)},E^{(\alpha,\beta)})$ such that :
	\begin{itemize}
		\item $V^{(\alpha,\beta)} = \{(u,\gamma) | u \in V, \gamma \in \{\alpha,\beta\} \} \cap V_M$
		\item $W^{(\alpha,\beta)}= \{(t,u,\gamma) | u \in V, \gamma \in \{\alpha,\beta\} \} \cap W_M$
		\item $E^{(\alpha,\beta)} = \{(t,(u,\alpha),(v,\beta) | u,v \in V\} \cap E_M $
	\end{itemize}
	\pimprenelle{fin}
    Notice that for any layer $i$, $S^{(i)}$ is equivalent to $S^{(i,j)}$.
